% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Amir Arsalan Yavari}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: \href{mailto:aa.yavari@ce.sharif.edu}{aa.yavari@ce.sharif.edu}     &
\hspace{0.4in} \textbf{GitHub}: \href{https://www.github.com/arsalanyavari}{github.com/arsalanyavari}  \\

% Line 2: Phone number, LinkedIn, citizenship
\textbf{Website}: \href{https://www.amirarsalanyavari.info}{AmirArsalanYavari.info}  & 
\hspace{0.4in} \textbf{LinkedIn}: \href{https://www.linkedin.com/in/amir-arsalan-yavari}{linkedin.com/in/amir-arsalan-yavari}

\end{tabular}
\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

\nohyphens{\color{MidnightBlue}{Research interests}}
& Cloud - Fog Computing, Computer Networking, DevOps Engineering \\
& \\

% --- Section: Education ---

\color{MidnightBlue}{Education} 
& \textbf{Sharif University of Technology (SUT)} \hfill Tehran \\ 
& Master's degree student in the field of Fog Computing \hfill 2023 -- 2025 \\
& Supervisors: Dr. Ali Movaghar and Dr. Shaahin Hessabi  \\
& \\

& \textbf{Isfahan University of Technology (IUT)} \hfill Isfahan \\ 
& Bachelor's degree in Secure Computing GPA: 3.6/4 \hfill 2019 -- 2023 \\
& Supervisor: Dr. Elham Mahmoudzadeh \\
& Project title: Automating Software Repair (fix software semantic bug) \\
& \\

% --- Section: Teaching experience ---

{\color{MidnightBlue}{Teaching experience}} 
& \textbf{Teaching assistants in SUT} \hfill Dec 2023 - Present \\
& I was a teaching assistant of \textbf{Computer Networking} under the supervision of Dr. K. Mizanian and 
 \textbf{Logical Design and Circuits} under the supervision of Dr. S. Hessabi. \\
& My responsibilities included Designing assignments and grading students' assignments.\\
& \\

& \textbf{Network Laboratory Supervisor, Department of Computer} \hfill Winter 2023 \\
& I was a supervisor in the Computer Networks laboratory under the guidance of Dr. A. Fanian and Dr. M. Heidarpour at Isfahan University of Technology.\\
& My responsibilities included designing and preparing the laboratory agenda, conducting laboratory meetings, and designing as well as administering exams.\\
& \\

& \textbf{OS Laboratory Supervisor, Department of Computer} \hfill Fall 2022 \\
& I was one of the supervisors in the Operating System laboratory under the guidance of Dr. M. Heidarpour and Dr. Z. Zali at Isfahan University o Technology.\\
& My responsibilities included holding laboratory meetings, grading students' assignments, and conducting exams.\\
& \\

& \textbf{Teaching assistants in IUT} \hfill Sep 2021 - Jul 2023 \\
& I was a teaching assistant of \textbf{Computer Networking}, \textbf{Operating Systems} and \textbf{Algorithm Design} under the supervision of Dr M.heidarpour, \textbf{Data Structure} and \textbf{Fundamental of Programming} under the supervision of Dr. S.Hosseini, \textbf{Operating Systems} under the supervision of Dr. Z.Zali and \textbf{Advanced Programming} under the supervision of Dr. S.Bagholizadeh. \\
& My responsibilities included Designing assignments and projects, Grading students' assignments, conducting exercise-solving classes.\\
& \\

% --- Section: Industry experience ---

{\color{MidnightBlue}{Industry experience}} 
& {\textbf{Ergo Platform}} Rosen Bridge Project \hfill \\
& DevOps Engineer and System Administrator \hfill Spring 2023 \\
& As a DevOps Engineer, my primary responsibilities included deploying programs using Docker and implementing CI/CD pipelines. Additionally, I managed Proxmox VMs, configured the organization's internet, and set up monitoring and logging systems.\\
& \\
 
% --- Section: Talks and tutorials ---

{\color{MidnightBlue}{Talks and tutorials}} 
& \textbf{DevOps and CI/CD} \hfill Sep 2023 \\
& The webinar, focused on DevOps culture and automation, specifically Continuous Integration (CI), was organized by the Isfahan University of Technology as part of the AICup event. \\
& \\

& \textbf{Linux Day} \hfill Aug 2022 \\
& The webinar, centered around Linux, was organized by the Isfahan University of Technology Computer Engineering Students Scientific Association. \\
& \\

& \textbf{Linux Workshop} \hfill  Apr 2022 \\
& The workshop, organized by the Isfahan University of Technology Computer Engineering Students Scientific Association, covered topics related to Linux Essentials. \\
& \\

% --- Section: Various skills (programming, software, languages, etc.) ---

{\color{MidnightBlue}{Skills}} 
& \textbf{Programming}\\
& \\

& \textbf{System Administrating and Containerization}\\
& \\

& \textbf{Process Automating}\\
& \\

& \textbf{Languages} \\
& English (fluent), Persian (mother tongue) \\
& \\

% --- Section: Volunteer Activities ---

\color{MidnightBlue}{Volunteer Activities}
& \textbf{IUT CESSA Chair Person} \hfill Oct 2021 - Dec 2022 \\
& I was the head of the Computer Engineering Student Scientific Association in Isfahan University of Technology. \\
& \\

& \textbf{Technical Team Leader} \hfill Oct 2021 - Nov 2021 \\
& I was the Frontend, Backend and DevOps teams leader in Isfahan University of Technology Collegiate Programming Contest 2021. \\
& \\

& \textbf{APACHEE Club Central Council} \hfill Feb 2021 - Oct 2021 \\
& I was a member of the APACHEE Club at Isfahan University of Technology. \\
& \\

% --- End of CV! ---

\end{longtable}
\end{document}

